Robust positively invariant sets for state dependent and scaled disturbances

### 2015-03-19 draft.tex
test
Nothing really.

Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets.
%By ${\bf{1}}$ we denote 
Also ${\bf{1}}$ denotes the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 

>>>>

Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half 
spaces as polyhedra, and to bounded polyhedra as polytopic sets. ${\bf{1}}$ denotes the column vector of 
ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 
